---
title: "Data Visualization and Statistical Analysis"
author: "Juliana Rosa"
date: "19/04/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Dataframes created on the data_ingestion_wrangling_mc, and data_ingestion_wrangling_us scripts will be used here.
```

```{r}
#Loading packages
library(dplyr)
library(ggplot2)
library(lubridate)
library(questionr)
library(readxl)
library(vcd)
library(plotly)
library(gridExtra)
```

```{r}
#Importing clean mc data (previously created)
hc_mc <- read_excel("hc_mc.xlsx")
hc_mc_comp <- read_excel("hc_mc_comp.xlsx")
```

```{r}
#Assigning appropriate data types
hc_mc$victim_count <- as.integer(hc_mc$victim_count)
hc_mc$suspect_count <- as.integer(hc_mc$suspect_count)
hc_mc$suspects_less_than_18_years <- as.integer(hc_mc$suspects_less_than_18_years)
hc_mc$suspects_18_35_years_old <- as.integer(hc_mc$suspects_18_35_years_old)
hc_mc$suspects_36_45_years_old <- as.integer(hc_mc$suspects_36_45_years_old)
hc_mc$suspects_46_55_years_old <- as.integer(hc_mc$suspects_46_55_years_old)
hc_mc$suspects_55_years_old <- as.integer(hc_mc$suspects_55_years_old)
```

```{r}
#Importing clean us data (previously created)
hc_us <- read_excel("hc_us.xlsx")
hc_us_comp <- read_excel("hc_us_comp.xlsx")
```

```{r}
#Assigning appropriate data types
hc_us$victim_count <- as.integer(hc_us$victim_count)
hc_us$offender_count <- as.integer(hc_us$offender_count)
hc_us$adult_offenders <- as.integer(hc_us$adult_offenders)
hc_us$juvenile_offenders <- as.integer(hc_us$juvenile_offenders)
```

#Question 1: How are the variables “bias code”, “offense”, and “victim type” related?

```{r}
#bias_code vs offense

##Standard two-way table
table(hc_mc$bias_code, hc_mc$offense)

##Frequencies divided by the "row total"
round(prop.table(table(hc_mc$bias_code, hc_mc$offense), margin=1), digits=5)*100

##"Column totals" divided by "general total"
round(colSums(table(hc_mc$bias_code, hc_mc$offense)), digits=5)*100/sum(rowSums(table(hc_mc$bias_code, hc_mc$offense)))

##Independency Test and Measures of Association
summary(assocstats(table(hc_mc$bias_code, hc_mc$offense)))
```


```{r}
#bias_code vs victim_type

##Standard two-way table
table(hc_mc$bias_code, hc_mc$victim_type)

##Frequencies divided by the "row total"
round(prop.table(table(hc_mc$bias_code, hc_mc$victim_type), margin=1), digits=5)*100

##"Column totals" divided by "general total"
round(colSums(table(hc_mc$bias_code, hc_mc$victim_type)), digits=5)*100/sum(rowSums(table(hc_mc$bias_code, hc_mc$victim_type)))

##Independency Test and Measures of Association
summary(assocstats(table(hc_mc$bias_code, hc_mc$victim_type)))
```


```{r}
#offense vs victim_type

##Standard two-way table
table(hc_mc$offense, hc_mc$victim_type)

##Frequencies divided by the "row total"
round(prop.table(table(hc_mc$offense, hc_mc$victim_type), margin=1), digits=5)*100

##"Column totals" divided by "general total"
round(colSums(table(hc_mc$offense, hc_mc$victim_type)), digits=5)*100/sum(rowSums(table(hc_mc$offense, hc_mc$victim_type)))

##Independency Test and Measures of Association
summary(assocstats(table(hc_mc$offense, hc_mc$victim_type)))
```


#Question 2: Is there an association between victim and suspect count?

##MC

```{r}
#Scatterplot
ggplot(hc_mc_comp, aes(suspect_count, victim_count))+
  geom_jitter(alpha=0.5, color="brown4")+
  geom_smooth(method=lm, color="brown4", se=FALSE)+
  theme_light()+
  labs(x="Suspect Count", y="Victim Count")+
  ggtitle("Relationship Between Suspect and Victim Count", subtitle="Montgomery County")

#Testing linear relationship
cor.test(hc_mc_comp$suspect_count, hc_mc_comp$victim_count, method="spearman")
cor.test(hc_mc_comp$suspect_count, hc_mc_comp$victim_count, method="pearson")

#linear regression model
mod <- lm(victim_count~suspect_count, data=hc_mc_comp)
coef(mod)
anova(mod)
```

##US

```{r}
#Scatterplot
ggplot(hc_us_comp%>%filter(victim_count!=200), aes(suspect_count, victim_count))+
  geom_jitter(alpha=0.5, color="brown4")+
  geom_smooth(method=lm, color="brown4", se=FALSE)+
  theme_light()+
  labs(x="Offender Count", y="Victim Count")+
  ggtitle("Relationship Between Offender and Victim Count", subtitle="United States")+
  scale_x_continuous(breaks=c(0, 2, 4, 6, 8, 10, 12, 14, 16, 18, 20, 22, 24, 26, 28, 30))

#Testing linear relationship
cor.test(hc_us_comp$suspect_count, hc_us_comp$victim_count, method="spearman")
cor.test(hc_us_comp$suspect_count, hc_us_comp$victim_count, method="pearson")

#linear regression model
mod1 <- lm(victim_count~suspect_count, data=hc_us_comp)
coef(mod1)
anova(mod1)
```


#Question 3: Does the distribution of incidents by state follow a similar pattern to the population proportion of each state?

```{r}
#Importing dataset with states' populations in proportion to the country's population
#Source of data: https://www.infoplease.com/us/states/state-population-by-rank
#The data were copied from the link above and pasted into excel
#Before importing it into R, I just changed "DC" to "District of Columbia" and saved the file as pop_states.xlsx
#The excel file is available on my repo
pop_states <- read_excel("population_states.xlsx")

#Renaming columns
pop_states <- pop_states%>%
  rename(state='State', pop_prop='Percent of Total', pop=Population)

#Ordering states by population proportion
pop_states$state <- factor(pop_states$state, levels=c("California", "Texas", "Florida",
                                                      "New York", "Illinois",
                                                      "Pennsylvania", "Ohio", "Georgia",
                                                      "North Carolina", "Michigan",
                                                      "New Jersey", "Virginia",
                                                      "Washington", "Arizona",
                                                      "Massachusetts", "Tennessee",
                                                      "Indiana", "Missouri", "Maryland",
                                                      "Wisconsin", "Colorado",
                                                      "Minnesota", "South Carolina",
                                                      "Alabama", "Louisiana", "Kentucky",
                                                      "Oregon", "Oklahoma",
                                                      "Connecticut", "Utah", "Iowa",
                                                      "Nevada", "Arkansas",
                                                      "Mississippi", "Kansas",
                                                      "New Mexico", "Nebraska",
                                                      "West Virginia", "Idaho", "Hawaii",
                                                      "New Hampshire", "Maine",
                                                      "Montana", "Rhode Island",
                                                      "Delaware", "South Dakota",
                                                      "North Dakota", "Alaska",
                                                      "District of Columbia", "Vermont",
                                                      "Wyoming"), ordered=TRUE)
```

```{r}
##Ordering states by population
hc_us$state <- factor(hc_us$state, levels=c("California", "Texas", "Florida",
                                                       "New York", "Illinois",
                                                       "Pennsylvania", "Ohio", "Georgia",
                                                       "North Carolina", "Michigan",
                                                       "New Jersey", "Virginia",
                                                       "Washington", "Arizona",
                                                       "Massachusetts", "Tennessee",
                                                       "Indiana", "Missouri", "Maryland",
                                                       "Wisconsin", "Colorado",
                                                       "Minnesota", "South Carolina",
                                                       "Alabama", "Louisiana", "Kentucky",
                                                       "Oregon", "Oklahoma",
                                                       "Connecticut", "Utah", "Iowa",
                                                       "Nevada", "Arkansas",
                                                       "Mississippi", "Kansas",
                                                       "New Mexico", "Nebraska",
                                                       "West Virginia", "Idaho", "Hawaii",
                                                       "New Hampshire", "Maine",
                                                       "Montana", "Rhode Island",
                                                       "Delaware", "South Dakota",
                                                       "North Dakota", "Alaska",
                                                       "District of Columbia", "Vermont",
                                                       "Wyoming"), ordered=TRUE)

#Goodness of Fit Test
chisq.test(table(hc_us$state), p=pop_states$pop_prop, rescale.p=TRUE)

##Barplot
ggplot()+
  geom_bar(aes(x=hc_us$state, y = (..count..)/sum(..count..), fill="Incidents"), alpha=0.5)+
  geom_bar(aes(x=pop_states$state, y=pop_states$pop_prop, fill="Population"), stat='identity', alpha=0.5)+
  coord_flip()+
  scale_y_continuous(labels=scales::percent)+
  theme_light()+
  xlab("State")+
  ylab("Percentage")+
  ggtitle("Incidents and Population by State", subtitle="United States")+
  scale_fill_discrete(name="Colors")
```

#Question 4: Does the offender’s race tell us something about the bias code of the incident?

```{r}
#Colored Barplot
ggplot(hc_us%>%filter(!is.na(offender_race)), aes(bias_code, fill=offender_race))+
  geom_bar(position="dodge")+
  coord_flip()+
  theme_light()+
  ggtitle("Association between Bias and 
          Offender's Race")+
  xlab("Bias Code")+
  ylab("Incidents")+
  theme(axis.text.x = element_text(angle=45))+
  scale_fill_manual("Offender's Race", values=c("yellow", "orange", "red", "green", "blue", "purple"))

##Independency Test and Measures of Association
summary(assocstats(table(hc_us$offender_race, hc_us$bias_code)))
```

#Question 9: How have bias incidents changed over the years in Montgomery County? How is that different from the national scenario?

```{r}
#bias code over the years

##MC
ggplot(hc_mc_comp, aes(bias_code, fill=as.character(year)))+
  geom_bar(alpha=0.8)+
  coord_flip()+
  facet_wrap(~year)+
  theme_light()+
  theme(legend.position = "none")+
  labs(x="Bias Code", y="Incidents")+
  ggtitle("Bias Codes Over the Years", subtitle="Montgomery County")

##US
ggplot(hc_us_comp, aes(bias_code, fill=as.character(year)))+
  geom_bar(alpha=0.8)+
  coord_flip()+
  facet_wrap(~year)+
  theme_light()+
  theme(legend.position = "none")+
  labs(x="Bias Code", y="Incidents")+
  ggtitle("Bias Codes Over the Years", subtitle="United States")
```

```{r}
#offense over the years

##MC
ggplot(hc_mc_comp, aes(offense, fill=as.character(year)))+
  geom_bar(alpha=0.8)+
  facet_wrap(~year)+
  theme_light()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 30))+
  labs(x="Offense", y="Incidents")+
  ggtitle("Offenses Over the Years", subtitle="Montgomery County")+
  scale_fill_brewer(palette = "Set1")

##US
ggplot(hc_us_comp, aes(offense, fill=as.character(year)))+
  geom_bar(alpha=0.8)+
  facet_wrap(~year)+
  theme_light()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 30))+
  labs(x="Offense", y="Incidents")+
  ggtitle("Offenses Over the Years", subtitle="United States")+
  scale_fill_brewer(palette = "Set1")
```

```{r}
#victim type over the years

##MC
ggplot(hc_mc_comp, aes(victim_type, fill=as.character(year)))+
  geom_bar(alpha=0.8)+
  coord_flip()+
  facet_wrap(~year)+
  theme_light()+
  theme(legend.position = "none")+
  labs(x="Victim Type", y="Incidents")+
  ggtitle("Types of Victims Over the Years", subtitle="Montgomery County")+
  scale_fill_brewer(palette = "Dark2")

##US
ggplot(hc_us_comp, aes(victim_type, fill=as.character(year)))+
  geom_bar(alpha=0.8)+
  coord_flip()+
  facet_wrap(~year)+
  theme_light()+
  theme(legend.position = "none")+
  labs(x="Victim Type", y="Incidents")+
  ggtitle("Types of Victims Over the Years", subtitle="United States")+
  scale_fill_brewer(palette = "Dark2")
```


```{r}
#case status over the years for mc
hc_mc%>%
  plot_ly(x=~jitter(suspect_count), y=~jitter(victim_count), color=~case_status)%>%
  layout(title = "Case Status Over the Years",
         xaxis = list(title = "Suspect Count"), yaxis = list(title = "Victim Count"))%>%
  add_markers(frame=~year(incident_date), colors = c("red", "blue", "yellow"))%>%
  animation_opts(frame=2500, transition=2000)%>%
  animation_slider(currentvalue=list(prefix=NULL))
```



#Question 10: Is there a pattern on the frequency of incidents over the months?

```{r}
#Month

p1 <- ggplot(hc_mc%>%filter(year(incident_date)%in%c(2016, 2017)))+
  geom_freqpoly(bins=12, aes(month(incident_date),
                             color=as.character(year(incident_date))), size=1)+
  theme_light()+
  scale_color_manual(values=c("darkred", "darkblue"))+
  ylim(0, 20)+
  theme(legend.position = "none", axis.text.x = element_text(angle = 45))+
  geom_text(aes(13, 13, label="2016"), color="darkred")+
  geom_text(aes(11.5, 7.5, label="2017"), color="darkblue")+
  labs(x="Month", y="Incidents")+
  ggtitle("Bias Incidents Over Time")+
  scale_x_continuous(breaks=c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),
                     labels=c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))


p2 <- ggplot(hc_mc%>%filter(year(incident_date)%in%c(2018, 2019)))+
  geom_freqpoly(bins=12, aes(month(incident_date),
                             color=as.character(year(incident_date))), size=1)+
  theme_light()+
  scale_color_manual(values=c("darkgoldenrod2", "purple"), name="Year")+
  ylim(0, 20)+
  theme(legend.position = "none", axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text(angle = 45))+
  geom_text(aes(12, 11, label="2018"), color="darkgoldenrod2")+
  geom_text(aes(11, 7, label="2019"), color="purple")+
  labs(x="Month", y="")+
  ggtitle("")+
  scale_x_continuous(breaks=c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),
                     labels=c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))


p3 <- ggplot(hc_mc%>%filter(year(incident_date)%in%c(2020, 2021)))+
  geom_freqpoly(bins=12, aes(month(incident_date),
                             color=as.character(year(incident_date))), size=1)+
  theme_light()+
  scale_color_manual(values=c("chartreuse4", "darkorange2"), name="Year")+
  ylim(0, 20)+
  theme(legend.position = "none", axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text(angle = 45))+
  geom_text(aes(12, 11, label="2020"), color="chartreuse4")+
  geom_text(aes(11, 1, label="2021"), color="darkorange2")+
  labs(x="Month", y="")+
  ggtitle("")+
  scale_x_continuous(breaks=c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),
                     labels=c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))


grid.arrange(p1, p2, p3, nrow = 1)
```

#Recommendations

```{r}
ggplot(hc_mc%>%filter(!is.na(suspect_count)), aes(suspect_count, fill=offense))+
  geom_bar()+
  facet_grid(~offense)+
  scale_fill_brewer(palette = "Dark2")+
  theme_light()+
  labs(x="Suspect Count", y="Incidents")+
  theme(legend.position = "none")+
  ggtitle("Number of Suspsects for Different Offenses", subtitle="Montgomery County")
```

